Clicks and Cliques

### 2018-12-18 papersoul.Rnw
code change in data chunk

% All chunks that make models or data procesing, at the begining
<<setup, include=FALSE, cache=FALSE,warning=FALSE,message=FALSE>>=
options(replace.assign=TRUE,width=50)
opts_chunk$set(fig.path='figure/graphics-', cache.path='cache/graphics-', fig.align='center', fig.width=8, fig.height=5, fig.show='hold', cache=TRUE, par=TRUE)
knit_hooks$set(par=function(before, options, envir){
if (before && options$fig.show!= 'none') par(mar = c(4, 4, .1, .1), cex.lab = .95, cex.axis = .9, mgp = c(2, .7, 0), tcl = -.3)
}, crop = hook_pdfcrop)

@@

# to be removed...
library(reshape2)
library(plyr)

@@

Sys.setenv(TEXINPUTS=getwd(),
           BIBINPUTS=getwd(),
           BSTINPUTS=getwd())
@

<<data,echo=FALSE,warning=FALSE,message=FALSE, cache=FALSE>>=
# Procesing data sets from SOCT and Census Bureau
source('code/data_chk_tidy.R')
source('code/census_chk.R')

# Compute comunity proportion of attached people
lev <- levels(soul$QSB)
census.data %<>%
        mutate(QSB = factor(census.data$QSB, labels=sort(lev)) ) %>%
        left_join(att.pr[, c(1,2,4)], by = "QSB") %>% 
        mutate(QSB = reorder(QSB, CCEGRP2Attached))

# loading results from cluster and random forest models. 
load('data/res_cluster.Rdta')
load('data/res_rf.Rdta')
soul.red2$cl.id <- factor(km$cluster)
rankings <- ddply(subset(important, rnk < 6), .(dim, rnk), function(x) length(x$dim))
rankings$rnk <- as.factor(rankings$rnk)
levels(rankings$rnk) <- paste("R", 1:5, sep = "")
@

>>>>

% All chunks that make models or data procesing, at the begining
<<setup, include=FALSE, cache=FALSE,warning=FALSE,message=FALSE>>=
options(replace.assign = TRUE, width = 50)
opts_chunk$set(fig.path = 'figure/graphics-', cache.path = 'cache/graphics-', fig.align = 'center', fig.width = 8, fig.height=5, fig.show = 'hold', cache = FALSE, par = TRUE)
knit_hooks$set(par = function(before, options, envir){
if (before && options$fig.show!= 'none') par(mar = c(4, 4, .1, .1), cex.lab = .95, cex.axis = .9, mgp = c(2, .7, 0), tcl = -.3)
}, crop = hook_pdfcrop)

@@

# to be removed...
#library(reshape2)
library(plyr)

@@

Sys.setenv(TEXINPUTS = getwd(),
           BIBINPUTS = getwd(),
           BSTINPUTS = getwd())
@

<<data,echo=FALSE,warning=FALSE,message=FALSE, cache=FALSE>>=
# Procesing data sets from SOCT and Census Bureau
source('code/data_chk_tidy.R')
source('code/census_chk.R')
# loading results from cluster and random forest models.

res_cluster <- readRDS('data/res_cluster.rds') %>% 
  list2env(globalenv())

res_rf <- readRDS('data/res_rf.rds') %>% 
  list2env(globalenv())

# Compute comunity proportion of attached people
lev <- soul %>% pull(QSB) %>% levels()
census.data %<>%
        mutate(QSB = factor(census.data$QSB, labels = sort(lev))) %>%
        left_join(att.pr[, c("QSB", "CCEGRP2Attached", "CCEGRP2Not Attached")], by = "QSB") %>% 
        mutate(QSB = reorder(QSB, CCEGRP2Attached))

soul.red2 <- soul.red2 %>%
  mutate(cl.id = factor(km$cluster) )

rankings <- important %>% 
  filter( rnk < 6) %>% 
  group_by(dim, rnk) %>% summarize(V1 = length(dim)) %>%
  ungroup() %>% mutate(rnk = factor(rnk, labels = paste("R", 1:5, sep = "") ))

@
